**Defining protein biomarkers for *Candida albicans* extracellular vesicles**

### 2019-02-04 manuscript/manuscript.Rmd
Update references.bib

---
title: "**Defining protein biomarkers for *Candida albicans* extracellular vesicles**"
author: "*Charlotte Dawson^a^, Mark Bleackley^a^, Marilyn Anderson^a^*"
date: "*^a^Department of Biochemistry and Genetics, La Trobe University, Victoria, Australia*"
output: 
    bookdown::word_document2:
      pandoc_args:
        '--lua-filter=templates/pagebreak.lua'
      reference_docx: "templates/draft_template.docx"
      fig_caption: yes
    html_notebook: default
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: references.bib
csl: "templates/molecular-and-cellular-proteomics.csl"
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \usepackage{lipsum}
  - \pagestyle{fancy}
  - \fancyhead[L]{This is the running title it is rather long}
---

@@

Here is a citation [@Marwick2017]

>>>>

---
title: "**Defining protein biomarkers for *Candida albicans* extracellular vesicles**"
author: "*Charlotte Dawson^a^, Mark Bleackley^a^, Marilyn Anderson^a^*"
date: "*^a^Department of Biochemistry and Genetics, La Trobe University, Victoria, Australia*"
output: 
    bookdown::word_document2:
      pandoc_args:
        '--lua-filter=templates/pagebreak.lua'
      reference_docx: "templates/draft_template.docx"
      fig_caption: yes
    html_notebook: default
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: references.bib
csl: "templates/molecular-and-cellular-proteomics.csl"
link-citations: yes
linkcolor: blue
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \usepackage{lipsum}
  - \pagestyle{fancy}
  - \fancyhead[L]{This is the running title it is rather long}
---

@@

Here is a citation [@marwick2017].
